\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Assignment 6. Probability distributions}
\author{Your name}

\begin{document}
\maketitle


Solve the following problems -- each problem on a separate page -- and submit to Gradescope for grading. 

\newpage
\section{Poisson [4 points]}
In a certain factory accidents occur at a mean rate of 2 per week. Find the probability of less than 3 accidents occurring in a given month.


Show steps of your computation.

\newpage
\section{Normal distribution [4 points]}
Replacement time for the cell phone devices due to failure is normally distributed with a mean of $\mu=8.2$ years and standard deviation of $\sigma = 1.1$ years. 
\begin{itemize}
    \item (a) What is the probability that a randomly selected device will be replaced in less than 5 years?
    \item (b) As a manufacturer, what period of warranty should I declare if I want only 1\% of my devices to fail during the warranty period?
\end{itemize}


For a final answer you can use the values in the tables.

However, for a full grade please explain your reasoning: do not just give a numeric answer. 

\newpage
\section{Naive Bayes with numeric attributes [6 points]}
The historical data about tax evasion is presented in the table below:
\begin{center}
\begin{tabular}{ |c|c|c|c|c| } 
 \hline
Tid & Refund & Marital status & Taxable income & Evade \\
 \hline
1 & Yes & Single & 125K & No \\
2 & No & Married & 100K & No \\ 
3 & No & Single & 70K & No \\ 
4 & Yes & Married & 120K & No \\ 
5 & No & Divorced & 95K & Yes \\ 
6 & No & Married & 60K & No \\ 
7 & Yes & Divorced & 220K & No \\ 
8 & No & Single & 85K & Yes \\ 
9 & No & Married & 75K & No \\ 
10 & No & Single & 90K & Yes \\ 
 \hline
\end{tabular}
\end{center}

Use Naive Bayes classifier to predict the tax evasion for the following record:

Classify: $(_, No, Married, 95K, ?)$

Apply the Laplace normalization for categorical attributes. 

Also provide the actual probability of cheating in your answer.\\


Show your steps.\\

I classify this record as: 

The probability of tax evasion is:

\end{document}



